\chapter{Abstract}

A smart contract is a program running on a blockchain platform.
Businesses often use it as a signed contract or an agreement to regulate the stakeholders
because smart contracts reduce the need in trusted intermediators, arbitrations, and enforcement costs.
Since there are existing conventional applications running business logic,
and coding smart contracts is a big barrier even for senior developers,
it's ideal to transform these applications to smart contracts.
Most of these existing applications are open source, thus it is feasible to obtain the functional implementation and run the transformation.

I will focus my work on Hyperledger Fabric,
which is a mature blockchain platform, allows smart contracts to be written in Java, and is permissioned.
This platform is preferred by businesses.

Not all conventional applications can be safely transformed to smart contracts.
Thus in this paper we propose to identify the patterns of conventional applications and tell which is transformable.
A mathematical model, e.g., rCOS and partial order, will be needed to formally describe the smart contract or the interactions so that certain properties can be proved.
Next I will use a neural network to classify the conventional applications into different categories, some of which are transformable.
Finally I implement algorithms to transform these applications to smart contracts.
My work is based on RM2PT, which transforms requirement documents to Java desktop application. I will reuse its rules and transform to smart contract.


The contributions of my work will be the following:
1) I propose a neural network architecture to analyze program source and classify them. The neural network will tell if a program can be transformed to smart contract.
2) I extend RM2PT and use formal methods to transform conventional applications to smart contract.
3) I propose a neural network architecture to do the same transformation.
4) I propose a model to describe smart contracts and the differences to conventional applications.



\textbf{\textit{Keywords ---}} neural networks, smart contract, blockchain