\chapter{Acknowledgements}

I acknowledge the generous financial support from Macao Polytechnic Institute.

I am indebted to my supervisor, Wei Ke, for his continued guidance and an endless supply of fascinating projects. His unassuming approach to research and science is a source of inspiration. This approach is reflected by his simple but clear writing style, which is something I hope to carry forward throughout my career.

I gratefully recognize the help of school director, Professor Rita Tse, who gives us opportunities of accessing the education of top universities in the world, including University of California, Los Angeles (UCLA), University of Coimbra, and University of Bologna.

%Thank you who arranged offices and facilities for us to study and research.

It is a key to strike a balance with life outside the dark depths of the lab. As such, I cannot stress enough about the importance of the retreats organized by programme coordinator Lam Chan Tong, including sports day, hiking, and BBQ at beach. He also consistently encouraged me to jump out of my comfortable zone.
%In fact, computers did most of the work in this thesis (they never get their due credit). I also had the pleasure of working with Rebecca Saaltink, who graciously showed me the ropes of her cloning apparatus.

%I am fortunate to have been a part of the CERC group. Thank you for the fun squash matches Kashif and Shayan, and thank you to my officemates for the lively physics conversations (especially Akbar, who always asked difficult yet simple questions).


Most importantly, I am grateful for my family's unconditional, unequivocal, and loving support.