\chapter{Problem Formulation}

\section{Research Problems}

Blockchain technology is a ground-breaking innovation in decentralized information technology.
A smart contract is a program running on a blockchain platform.
Businesses like using it as a signed contract or an agreement to regulate the stakeholders for various benefits.
However, it is often a big barrier for developers when they rewrite existing applications into smart contracts~\cite{dao2019challenges}.
Once a smart contract is deployed, it's hard to revise it.
Hence, developers need to implement smart contracts correctly in one shot.

Generally speaking many factors affect the tech stack of smart contracts.
Developers have to decide the data storage, consensus algorithm, throughput, and so on.
For instance, Bitcoin only approves 7 transactions per second~\cite{croman2016scaling} and thus cannot support a high volume smart contract.
To eliminate these variables, I will focus my work on Hyperledger Fabric, which is a preferred platform by businesses.

Because RM2PT transforms a requirement document into a Java desktop program, we will extend RM2PT so that it can generate smart contracts.
RM2PT includes a syntax parser and a set of rules.
I will add a post-processing plugin named RM2Hyperledger to transform conventional applications to smart contracts.
RM2\-Hyperledger also uses fixed rule set as a first step.

The problem is that I have to abstract the rules and leave out tiny implementation details so that everyone can understand.
Formal methods should be used here.
I will present the rules as inference rules in the form of~\autoref{inference-rule}. $R_0$ is the rule number.
If we meet the specified condition and a conventional application has source code $c$, we will apply $R_0$ and the corresponding smart contract code becomes $c'$.
I will use the following symbols in inference rules. $\mathbb{E}$ means entity classes. $E$ is a specific entity class.
$\mathbb{C}$ means contract classes.
$\mathbb{T}$ means transaction functions.

\begin{equation}\label{inference-rule}
R_0:\quad \frac{c}{c'} \quad \text{condition}
\end{equation}

Since there is no clear methodology for evaluating smart contract, RM2\-Hyper\-ledger will be evaluated on RM2PT's dataset with my own test cases,
we will check how many test cases passed.

Because some conventional applications are not suitable for smart contract,
I will use neural network to identify the application and classify it into regular application, randomness-based application,
high throughput application, secret in plain text, and other categories.
Only regular applications can be safely transformed into smart contract.
My network uses layers including transformer, neural machine translation, and LSTM. The network will be trained on Jiang's dataset consisting of \num{1006} software projects along with their git commits.

After we have implemented RM2Hyperledger our pipeline is not yet end-to-end. We had to first use neural network to classify programs, then switch to use traditional syntax-based rules.
RM2\-Hyperledger being a baseline, I will propose a neural network architecture to do the same transformation.
The proposed neural network is a generative model in Natural Language Processing that generates new source code.
This network will use BERT and word2vec.


The last but least problem is to propose a mathematical model to formally describe smart contracts and their differences to conventional applications.
I use finite state machine to model the state transition of smart contract because adding new blocks to the chain is a state transition.
I use total order and partial order to model the transformation from conventional applications to smart contract.
Each revision to the application should not break the application and add more functions to support blockchain.
We define the new version of the application $v_{i+1}$ and the old one  $v_i$, we will have partial order  $v_{i+1} > v_i $ meaning the new version is better than the old version.
I also use rCOS to formally specify smart contract, focusing on mathematical characterization of object-oriented concepts.
rCOS equations are like~\autoref{rcos}. $ ok \wedge p(x) \Rightarrow ok' \wedge R(x,x')$ means if a program is started properly ($ok$), and its input $x$ meets a predicate $p(x)$; then the program must terminate properly ($ok'$) and meet a postcondition $R(x,x')$.
We thus use shorthand $(p(x)\vdash R(x,x'))$ to denote this property.

\begin{equation}\label{rcos}
(p(x)\vdash R(x,x')) = ok \wedge p(x) \Rightarrow ok' \wedge R(x,x')
\end{equation}



%In terms of data storage
%1. The number of input databases.
%2. Model type of each input database.
%3. Mechanism for data transformation.




%In the requirements elicitation phase, developers have to clarify requirements, find errors or oversights in the requirements, where a lot of elbow grease is required. Then the development goes to the coding phase. Besides adding functions, developers have to review each other's code, do refactoring, and keep the codebase clean. Maintaining the codebase is another hard work.


\section{Aims and Objectives}

Businesses are already using conventional software to help deal with their business logic.
Some of these software are open source and hosted on GitHub.
Since these software are typically well-tested, we can transform these applications into smart contracts and we will save a lot of labor and get our implementation error-free.

Although Bitcoin and Ethereum are both popular platforms, I want to focus on smart contracts on Hyperledger Fabric.
Hyperledger Fabric is a permissioned network and there are authorities controlling who can join the network, thus preferred by businesses.
The smart contracts on Hyperledger Fabric can be developed in Java, NodeJS, or Go.
In my research, I contemplate generating source code in Java because RM2PT transforms requirement documents into Java desktop programs,
and I should be able to reuse its rules to transform smart contracts.

To archive this, I should embark on characteristics of blockchains and smart contracts, find out which functional implementations are transformable to smart contracts.
Next, I will train classification neural networks to automatically identify which conventional implementations are transformable.
Then, during the next transformation phase, we can either transform based on fixed rule sets or use neural networks again.
Finally, the transformed smart contracts must be verified and safe and follow the original specifications.

I will bake the static analysis or runtime checking into the transformation or add them in a post-processing step.
The analysis will make sure the smart contracts do not have common bugs, e.g., reentrancy problems, coin stealing, etc.
I hope to find a (mathematical) model to formally describe the smart contract or the interactions so that certain properties can be proved.
rCOS~\cite{ke2012rcos} is a formal model-driven engineering method for component-based software, which I can apply to smart contract.
I can also define some partial order by refinement calculus to prove each conversion does not break pre- and post-conditions, etc.





%I want to find some way to help software development go smoothly and error-free, help developers write programs faster and reduce headache in maintaining the programs.

%I find it is desirable to have a tool that generates prototypes directly from requirements with much human intervention, so that requirement engineers can run the prototype and find issues in the requirements, consult with the clients, and fix the issues as early as possible.



%In the coding phase, code review is a key to enforce software quality, where one developer reviews another developer's code. The new code is typically organized in a pull request, a side branch.
%I believe code review can be made easy by assigning different types of reviews to different specialists. In a version control system, a commit can be represented by a diff, and I contemplate we can use diff to classify pull requests. \autoref{fig:example-diff} shows an example diff file, where we can see the declaration of class \code{Chars} is changed and there is no other refactoring.


\section{Relevance, Novelty and Originality}

\etal{Yang}~\cite{yang2019automated} proposed their own DSL for requirement document writing,  and their RM2PT program generates vanilla Java source code from the DSL. Since blockchain and smart contract are hot research topics, I want to extend RM2PT so that smart contract applications can be generated.

%Another limitation of RM2PT is that it stipulates that the requirement document to be written in a DSL. Many open source Java repositories only give the source code, but no requirement documents.

I will try to invent a technology that as long as one Java program is written in certain patterns, for instance Model-View-Controller, I'm able to transform it to a smart contract application, if it meets other blockchain-specific properties.

The transformation rules encoded in RM2PT is manually devised without much theoretical support. On one hand I can use artificial intelligence to find mappings between the source and the target, and generate rules automatically. On the other hand, I can study the theories behind smart contract, find out which local programs can be safely converted to smart contracts and which patterns they follow.



It is the current trend to use neural networks to analyze program source code.
Program analysis with traditional methods is still incapable of answering relatively simple questions, for example
 ``Is this code thread-safe?''~\cite{alexandru2017replicating},
which might be a relevant question to determine if the program is suitable for smart contract.
Consequently researchers gradually move away from the traditional methods to neural networks.
Researchers~\cite{xu2019commit,liu2019generating} embraced neural machine translation (NMT) in commit message generation.
NMT was originally used for translating a natural language to another, now found excelled at translating diff to commit messages.
Such an NMT approach has two major components, the encoder and the decoder.
The encoder reads the diff and encodes it to some internal matrix representation,
then the decoder transforms the internal representation to human readable text, i.e., the commit messages.
I do not find works use NMT for commit classification.


I will first need a rigid syntax parser for prototyping, then use neural networks to classify the source code of conventional applications.
The output of my network will be a percentage, indicating how confident my network is that the input belongs to a given label.



%Taking diff as algorithm input, program analysis is specialized to diff analysis.
%A few works in diff analysis start to embrace machine learning techniques.
%\etal{Loyola}~\cite{loyola2017neural} developed a neural network model to generate text description from diff files.
%Their work relies on a lexer that divides source code into tokens,
%thus it is not end-to-end machine learning.
%\etal{Macho}~\cite{macho2016predicting} employed a random forest classifier and categorized commits into forward engineering, re-engineering, corrective engineering and management.
%
%RefDiff~\cite{silva2020refdiff} and RMiner~\cite{tsantalis2018accurate} can detect refactoring types, including extract method, rename class, pull methods, etc. Nonetheless, they have to read complete content of the changed files before and after a commit in order to run a detection.
%
