\chapter{Schedules and Milestones}

\section{Schedules}


\begin{description}
   \item[July 2021]  I've submitted a paper on diff classification.
   \item[March 2022] At present, I'm working on smart contract generation and going to write a conference paper. I plan to submit the paper on March 2022.
   \item[December 2022]  Next, I will work on the theory part of smart contract. The paper may focus on refinement calculus and use pre-order or partial order in theory proofs. I plan to submit the paper on December 2022.
   \item[April 2023] Finally I shall commence writing my doctoral thesis and submit it on April 2023.
\end{description}


\section{Key milestones}

Conference list:
\begin{enumerate}
\item International Conference on Intelligent Data Engineering and Automated Learning (IDEAL)
\item IEEE/ACM International Conference on Automated Software Engineering (ASE)
\item IEEE DAPPS: \url{https://ieeedapps.net/}
\end{enumerate}

Journal list:
\begin{enumerate}
\item Frontiers of Computer Science
\item IEEE Transactions on Industrial Informatics
\item IEEE Transactions on Reliability
\end{enumerate}

\section{Potential publications}

Besides the papers listed in \autoref{sec:produced-publications}, the following are potential publications.

\begin{description}
\item[Paper] RM2Hyperledger: Automated Prototype Generation From Requirements Model to Hyperledger Smart Contract
\item[Journal] Refining Conventional Applications to Smart Contracts
\item[Paper] A Neural Architecture for Classifying Refactoring Types from Diff
\item[Doctoral Thesis] Identification of Functional Implementation in Conventional Applications and Transformation to Smart Contracts
\end{description}



